Papers

### 2025-03-31 papers.qmd
update

@@

>>>>

- Copeland, A., Dora, J., King, K., Stafford, T., & Field, M. (in press). Value-based decision-making in daily tobacco smokers following experimental manipulation of mood. *Experimental and Clinical Psychopharmacology* [preprint](https://osf.io/preprints/psyarxiv/5w4ap_v1)

@@

## 2025

- Vardal, O., Karapanagiotidis, T., Stafford, T., Drachen, A., & Wade, A. (2025). [Unsupervised identification of internal perceptual states influencing psychomotor performance](https://doi.org/10.1016/j.neuroimage.2025.121134). NeuroImage, 310, 121134. https://doi.org/10.1016/j.neuroimage.2025.121134
[[preprint](https://www.biorxiv.org/content/10.1101/2023.09.08.556817v2.abstract)]
